\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage[hidelinks]{hyperref}
    \usepackage[left=2cm, right=2cm, top=2cm]{geometry}
    \usepackage{longtable}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
    \vspace*{-40pt}

    

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Profile
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \vspace*{-2pt}
  \begin{center}
    {\Huge \scshape {Sayam Palrecha}}\\
    \vspace*{2pt}
    \href{mailto:sayampalrecha09@gmail.com}{sayampalrecha09@gmail.com} | \href{tel:9370091963}{9370091963} | Lonavala, Pune\\
    \vspace*{2pt}
    \textbf{\href{https://github.com/sayampalrecha}{GitHub | }}\textbf{\href{https://medium.com/@sayampalrecha09}{Blog | }}\textbf{\href{https://www.linkedin.com/in/sayampalrecha/}{Linkedin}}\\
  \end{center}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Education
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Education}
      \vspace{2mm}
      \textbf{D.Y Patil College Of Engineering, Akurdi}\hfill Akurdi, Pune\\
Bachelor Artificial intelligence And Data Science \hfill June 2020 - June 2024\\
{\sl CGPA: 8.75}\\
\vspace{2mm}
      \textbf{Ryewood International Junior College, Lonavala}\hfill Lonavala\\
HSC Science \hfill June 2018 - May 2020\\
{\sl Percentage: 73}\%\\
\vspace{2mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Experience
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Experience}
      \vspace{2mm}

      \textbf{Intel Ai Students Club | AI-ML Lead} \hfill Akurdi | July 2024 - Present\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item Utilising the OpenVino Toolkit from Intel.
\item Responsibilities include working with coordinators, articulating and addressing real-world issues, and developing technology solutions using the OpenVino Toolkit.
\item  This is helping me immensely with my Team-work, Public Speaking and Communication skills.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Skills
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \header{Skills}
  \vspace{2mm}
  \begin{longtable}{p{4cm}p{12cm}}
  Programming Languages: & Python \\
  Libraries/Frameworks: & Numpy, Pandas, Matplotlib, Seaborn, Scikit-Learn \\
  Tools / Platforms: & Tableau, Notion, Github \\
  \end{longtable}
  \vspace{1mm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %
    %     Projects
    %
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
      \header{Projects / Open-Source}
      \vspace{2mm}
      {\textbf{Fake-News-Detection-Using-Machine-Learning}}\textbf{ | \href{https://github.com/sayampalrecha/Fake-News-Detection-Using-Machine-Learning}{Link}}\hfill{\sl Machine Learning, Pandas, Python}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  This project compared 4 Machine Learning Algorithm and compared the them based on the classification report to check which algorithm is the best for finding out fake news.
\item  This project was made as our submission for the PBL project which I had worked along side with 3 other classmates of mine and also lead the team.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Heart Disease Prediction Model}}\textbf{ | \href{https://github.com/sayampalrecha/Heart\_Disease\_Model}{Link}}\hfill{\sl Python, Machine Learning, Pandas, Logistic regression}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  With this project I am aiming to solve the problem of heart disease in people.
\item  Dataset was taken from the website of UC Irvine.
\item  The Algorithm used was Logistic Regression to predict using the given input that whether a person will get a heart disease or not.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Sonar-Detection-Model}}\textbf{ | \href{https://github.com/sayampalrecha/sonar-detection-project}{Link}}\hfill{\sl Python, K-NN, Machine Learning}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item This project used K-nearest Neighbour.
\item  This predicted whether an object was rock or a mine the dataset contained result\textquotesingle{}s of 60 different frequencies.
\end{itemize}
          \vspace*{3mm}
      {\textbf{World-Population-Analysis}}\textbf{ | \href{}{Link}}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  Used the different library for data analysis and visualisation.
\item  Compared the population of USA and China from 1990 to 2020.
\end{itemize}
          \vspace*{3mm}
      {\textbf{Department-website}}\textbf{ | \href{https://isa-website-puce.vercel.app/}{Link}}\hfill{\sl Figma}\\
          \vspace{-3mm}
\begin{itemize} \itemsep -3pt
\item  Worked in the design team and used Figma to create design for the website.
\item  Worked with 3 other members and gave impressive before the deadline.
\end{itemize}
          \vspace*{3mm}



\header{Honors \& Awards}
      \vspace{2mm} 
      Participated at the Viz-a-thon which was conducted at VIIT. One of the first Data Visualization Hackathon in the Pune district.\\
\vspace*{1mm}

    \ 
    \header{ Research\Experience}
    \vspace{2mm} 
    I am also working under the guidance of Dr. Vinayak Kottawar our HOD on a survey paper focussing on Use of Machine Learning in Prediction of Chronic Obstructive Pulmonary Disease.\\
\vspace*{1mm}

  \ 
    \end{document}